---
title: "sentiment-analysis-for-tweets-in-ukraine-march-2022"
description: |
  Twitter is one of the many organizations and social media platforms that have been exploited by and misused by organizers and supporters on either side of the conflict. People hope to use the platform to express beliefs and ideas that are not verified or peer-reviewed. Textual data were collected to observe negative and positive sentiments in the collection of tweets during March 2022 about the conflict in Ukraine. It can come from a popular outlet or an unverified user. The data was cleaned and then categorized to extract sentiments from the textual data. The sentiments and ideas expressed were visualized with a dashboard.
author:
  - name: Dayvonn Jones
    url: https://dayvonnjones.netlify.app
date: 2022-05-24
output:
  distill::distill_article:
    self_contained: false
    
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    social: menu
    source_code: embed
    theme: readable
---
#Library Set UP#
```{r}
library(flexdashboard)
library(tidyverse,quietly=T)
library(data.table,quietly=T)
library(htmltools)
library(htmlTable,quietly=T)
library(viridis,quietly=T)
library(plotly,quietly=T)
library(scales,quietly=T)
library(crosstalk)
library(maps)
library(flexdashboard)
library(shiny)
library(knitr)
library(kableExtra)
library(tidyverse)
library(plotly)
library(crosstalk)
library(bslib)
library(shiny)
library(tidyverse)
library(quanteda)
library(quanteda.textplots)
library(sentimentr)
library(viridis)
library(dplyr)
library(tidytext)
library(textdata)
library(stringr)
library(janeaustenr)
library(esquisse)
library(ggplot2)
library(plotly)
library(quantmod)
library(lubridate)
library(wordcloud)
library(sentiment.ai)
```

About {data-navmenu="Explore"}
===================================== 

Column {data-width=200}
-------------------------------------

#About this Flex Dashboard#
Textual data analysis is an emerging field of NLP; This dashboard is an approach to understanding the sentiments and emotions of people in the war-zoned country using Twitter textual data. This dashboard is also an attempt to visualize the data efficiently and beautifully.

Column {data-width=800}
-------------------------------------

#Areas that are Covered#
```{r jan222017-map1,echo=F}
emotion <-read.csv("/Users/dayvonnjones/Documents/Data Visualization Final Project/emotion.csv")
sentiment <-read.csv("/Users/dayvonnjones/Documents/Data Visualization Final Project/sentiment.csv")
uk <- readxl::read_xlsx("/Users/dayvonnjones/Documents/Data Visualization Final Project/ukraine.xlsx")
uk <- rename(uk, Date = ï..Data.created_at)
shared_data <- uk %>%
  select(Date, sentiment.x, class.x, Data.retweet_count, Data.full_text, Data.user.screen_name, Data.url, phrase.x, Data.user.location) %>%
  mutate(sentiment.x = round(sentiment.x, 4)) %>%
  SharedData$new()

p <- shared_data %>% 
  plot_ly(type='scatter', mode = 'markers', x = ~Date, y = ~sentiment.x, color= ~class.x, colors=c("#FFD500","#005BBB"),size = ~Data.retweet_count, hovertemplate = paste("<b>Tweet: </b> <br>",uk$Data.full_text, "<br> <b>Tweet by: </b> @",uk$Data.user.screen_name,"<br> <b>Tweet Link: </b> ",uk$Data.url,"<br> <b>Retweets: </b> ",uk$Data.retweet_count,"<br> <b>Tweet Sentiment Score: </b>", uk$sentiment.x,"<br> <b>Sentiment Phrase: </b>", uk$phrase.x, "<br> <b>User Provided Location: </b>", uk$Data.user.location,"<br> <b>Tweeted on: </b> </br>", uk$Date), autosize = TRUE, title = "Sentiment Analysis for Tweets in March 2022, Ukraine",
                        xaxis = list(rangeslider = list(type = "date"), title = "Date"),
                        yaxis = list(title = "Sentiment Score"),
                        legend = list(title=list(text="Sentiment Class")))

                        

# Combining several selectors
bscols(widths = c(4, 6),
       list(
            filter_checkbox(id = "class", label = "Sentiment Class",
                    sharedData = shared_data, group = ~class.x),
            filter_select(id = "phrase", label = "Sentiment Phrase",
                    sharedData = shared_data, group = ~phrase.x),
            filter_slider(id = "slider_sc", label = "Sentiment Score",
                    sharedData = shared_data, column = ~sentiment.x)
      ),
       p)
```

Spatial Components {.storyboard data-navmenu="Explore"}
=========================================

#Most Mentioned Cities#
```{r}
shiny::includeHTML("/Users/dayvonnjones/Documents/Data Visualization Final Project/CM.html")
```

#User Provided GeoLocation#
```{r}
shiny::includeHTML("/Users/dayvonnjones/Documents/Data Visualization Final Project/UL.html")
```

Sentiment Analysis {.storyboard data-navmenu="Explore"}
===================================== 

#Emotions Count with nrc sentiment (syuzhet)#
```{r, eval=T}

col <- colorRampPalette(c("#ffd500", "#bfb72f", "#bfb72f", "#2b6f9c", "#005bbb"))
col2 <- colorRampPalette(c("#005bbb","#2b6f9c", "#bfb72f","#bfb72f", "#ffd500" ))

f1 <-  ggplot(emotion) +
   aes(x = reorder(phrase,-count), fill = class, weight = count) +
   geom_bar() +
   scale_fill_manual(values = c(negative = "#FFD500", 
  positive = "#005BBB")) +
   labs(x = "Emotion", y = "Frequency", title = "Tweet Emotions", subtitle = "Emotions counted by Positive-Negative Classes of tweets about Russia-Ukraine War; March 2022", caption = "Data visualization by Dayonn J., @DayvonnJ, Nilay V., @nilayvinchhi., Data source: Twitter API, produced using c(ggplot2, sentiment.ai, nrc sentiment) Libraries in R 4.1.3", 
   fill = "Sentiment Class") +
  geom_text(aes(x=reorder(phrase,-count), y = count, label = count), nudge_y=50)
ggplotly(p = f1)
```

#Sentiment Analysis with Bing Lexicon#
```{r}
text.sentiment <- tibble(text = str_to_lower(sentiment$phrase))

bing_word_counts <- text.sentiment %>% unnest_tokens(output = word, input = text) %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE)

bing_top_10_words_by_sentiment <- bing_word_counts %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n, n = 10) %>% 
  ungroup() %>% 
  mutate(word = reorder(word, n)) 

f2 <-  bing_top_10_words_by_sentiment %>% 
    ggplot(aes(word, n, fill = sentiment)) + 
    geom_col(show.legend = FALSE) + 
    facet_wrap(~sentiment, scales = "free_y") + 
    scale_fill_manual(values = c(negative = "#FFD500", 
  positive = "#005BBB"))+
      coord_flip()+
       labs(x = NULL, y = "Phrases contributing to Sentiment Class", title = "Phrases by Sentiment Class for Tweets", subtitle = "Phrases counted by Positive-Negative Classes of tweets about Russia-Ukraine War; March 2022", caption = "Data visualization by Dayonn J., @DayvonnJ, Nilay V., @nilayvinchhi., Data source: Twitter API, produced using c(ggplot2, nrc sentiment) Libraries in R 4.1.3")+
    geom_text(aes(x=word, y = n, label = n), nudge_y=10, color= "grey")+
  theme_minimal()

ggplotly(p = f2)

```

#Sentiment Analysis  using Loughran Lexicon#
```{r}
loughran_word_counts <- text.sentiment %>% unnest_tokens(output = word, input = text) %>%
  inner_join(get_sentiments("loughran")) %>%
  count(word, sentiment, sort = TRUE)

loughran_top_10_words_by_sentiment <- loughran_word_counts %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n, n = 10) %>% 
  ungroup() %>%
  mutate(word = reorder(word, n))

f3 <-  loughran_top_10_words_by_sentiment %>% 
    ggplot(aes(word, n, fill = sentiment)) + 
    geom_col(show.legend = FALSE) + 
    facet_wrap(~sentiment, scales = "free_y") + 
     coord_flip()+
      scale_fill_manual(values = c(negative = "#FFD500", positive = "#005BBB", uncertainty = "#eacb10", constraining = "#95a24e", litigious = "#55847d"))+
         labs(x = NULL, y = "Phrases contributing to Sentiments", title = "Phrases contributing to Sentiments for Tweets", subtitle = "Phrases counted by Sentiments of tweets about Russia-Ukraine War; March 2022", caption = "Data visualization by Dayonn J., @DayvonnJ, Nilay V., @nilayvinchhi., Data source: Twitter API, produced using c(ggplot2, tidytext, tidyverse, syuzhet) Libraries in R 4.1.3")+
      geom_text(aes(x=word, y = n, label = n), nudge_y=10, color= "grey")+
    theme_minimal()
ggplotly(p=f3)
```
